An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-04-01 Paper.tex
Updated date
Change footnote representation
This commit tweaks the source code for footnotes. It starts them on a
new line (with a comment eating the previous newline) and adds a space
and comment to close them. This representation makes line-wrapping work
better and makes the footnote self-contained in git.

\date{December 9, 2011}

@@

\oos\ tests are commonly used in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.\footnote{Other papers in this literature include
  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:12,ClM:12b},
  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
  reviews of this literature and additional references, see
  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
  \citet{CoD:11}, and \citet{Gia:11}} In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a martingale difference sequence.  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic appropriately.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.}

@@

Mixing window strategies is uncommon but needn't be. In most
applications, the null hypothesis imposes stability as well as equal
accuracy between the two models.  The benchmark model rarely allows
for breaks, parameter drift, or other forms of
instability,\footnote{Exceptions are \citepos{StW:07}
  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} but the
researcher is typically concerned about instability.  Indeed, concern
about instability is often given as a reason for doing an \oos\
analysis, especially with a short rolling window.\footnote{This
  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
  \cite{GiR:09,GiR:10}, among others.} A researcher could impose
stability on both models by using a recursive window or relax
stability for both by using a rolling window; either approach should
not affect the test's size, but may affect power.  But the researcher
could instead impose stability on the benchmark and relax it for the
alternative by using a recursive window for the benchmark and a
rolling window for the alternative model.  This approach could have a
power advantage and is similar in spirit to using a Likelihood Ratio
Test instead of an \textsc{lm} or Wald test, which depend on just the
restricted or unrestricted model respectively.

@@

This paper focuses on nested models, as they have received the most
attention in the empirical and theoretical literature, but the
statistic can be used with non-nested models as well.  This generality
is useful, since \citepos{Wes:96} results do not apply to non-nested
models if they both encompass the true \dgp,\footnote{\citet{ClM:11b}
  call this scenario, ``overlapping models.''} which is allowable
under the null: in the limit, both models will converge to the \dgp\
and give identical forecasts.  Consequently, the naive \oos\ $t$-test
is invalid, even after correcting the standard error if necessary to
reflect parameter uncertainty.  \citet{ClM:11b} show that the fixed
window \oos\ $t$-test remains normal for these models but the
recursive and rolling windows (with the window size increasing to
$\infty$) do not, and provide a procedure for pointwise (but not
uniformly) valid tests for the recursive and rolling windows and
uniformly valid tests for the fixed window.  The test proposed in this
paper is uniformly valid and places fewer assumptions on the models
under study and the true \dgp.

@@

This paper also presents a new result for the validity of block
bootstraps with \oos\ statistics, which is necessary to verify that
the StepM is valid.  Existing results on bootstrapping \oos\
statistics have some drawbacks.  \citet{Whi:00} and \citet{Han:05} use
the stationary bootstrap, but require the test sample to be much
smaller than the training sample, which obviously does not hold here.
\citet{CoS:07} relax that requirement, but make the statistic more
complicated than necessary by adjusting the objective function of the
bootstrapped statistic to center it correctly.\footnote{Their
  recentering is required for consistency and does not imply higher
  order accuracy.}  A parametric bootstrap, such as that used by
\cite{Mar:95}, \cite{Lut:99}, and \citet{ClM:12b}, is an alternative
method, but requires the benchmark model to be correctly specified.
Although I focus on the null hypothesis that the benchmark is
correctly specified, this paper's block bootstrap methods remain valid
when the benchmark is misspecified and are relatively easy to
implement.  So this paper's result for bootstrapping \oos\ statistics
considerably improves on existing procedures.

@@

\section{Out-of-Sample Model Comparisons}\label{sec:1}
This section presents the new \oos\ statistic.  I will present the
single-comparison statistic first and then extend it to multiple
comparisons.  Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
(Theorem~\ref{res:1} lists the assumptions formally).  In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudo-true
coefficient of the regression of $y_{t+1}$ on $x_t$ and define
$\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If the linear model is
correctly specified, so $\varepsilon_{t+1}$ is a martingale difference
sequence with respect to $\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t),
(x_{t-1}, v_{t-1}, y_{t-1}),\dots)$, then we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt\ (assuming that its variance is uniformly
positive) and is asymptotically normal as $P \to \infty$, with $R$ an
arbitrary starting value\footnote{It will be clear momentarily why the
  summation begins at $R+1$ instead of $1$.} and $P = T - R$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
\end{equation}

@@

\begin{rem}
  The statistic we present tests the null hypothesis that the forecast
  errors from the population version of the benchmark model are a
  martingale difference sequence.  This hypothesis may not be
  appropriate, depending on the loss function or utility function of
  interest.  If one wants to test the less restrictive null hypothesis that
  $y_{t} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$ but not
  necessarily an \mds, one can replace $\hat{S}_{ff}$, $\hat{S}_{fg}$
  and $\hat{S}_{gg}$ with their \hac\ counterparts.  
  Our statistic can also be modified to test implications of
  optimal forecasts under other loss functions
  \citep[see][]{PaT:07,PaT:07b}; the statistic should be expressed as
  a forecast encompassing test using the models' generalized forecast
  errors.\footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.}
  Again, Lemma~\ref{res:a5} can cover these other applications.
\end{rem}

@@

Since most empirical papers study more than one alternative model,
Theorem~\ref{sec:1} is of limited use on its own.\footnote{Moreover,
  we would need to account for the existence of multiple models even if
each paper only considered a single model, since there are many papers
studying the same data.}  It can, however, be
used as the basis for a procedure that allows researchers to make
multiple comparisons.  Before presenting a theoretical result, I will
discuss some issues related to multiple hypothesis testing.

Suppose we have the family of hypotheses, $H_1,\dots,H_J$.  It is
clear that testing each hypothesis individually will often have a
probability greater than the tests' nominal size of rejecting at least
once.\footnote{Unless the statistics used for each test are completely
  interdependent, the probability will be strictly greater than the
  nominal size.}  Econometricians, e.g. \citet{Whi:00},
\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:12b}, have emphasized
statistics that test families of hypotheses that control the
probability any hypothesis is rejected given that they all are true,
known as \textit{weak control of familywise error}
(\wfwe).\footnote{An exception is \citet{HHK:10} who combine
  \citepos{RoW:05} StepM with \citepos{Han:05} threshold rule to
  control \sfwe\ for certain families of one-sided tests.}  This paper
focuses instead on controlling the probability that at least one true
hypothesis is rejected given any combination of true and false
hypotheses, known as \textit{strong control of familywise error}
(\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
even though these papers only prove \wfwe, statistics based on
nonparametric block bootstraps \citep{Whi:00,Han:05} can be shown to
control \sfwe\ as well \citep[this follows directly from][]{RoW:05}
and those based on the parametric bootstrap \citep{ClM:12b} essentially
control \sfwe\ if the individual null hypotheses are strengthened
slightly as below (see conclusion~\ref{it:1} of Theorem~\ref{res:2} as
well as Remark~\ref{rem:2}).  \citet{HuW:10} propose that researchers
construct critical values from the asymptotic joint distribution of
the test statistics and this procedure can control \sfwe\ as long as there is a
consistent estimator of that distribution.

@@

This procedure exploits the fact that $R$ is finite in
Theorem~\ref{res:1} and that the expected block length will grow with
$T$.  Under these asymptotics, a growing proportion of the
rolling-window forecasts are the same if we bootstrap the forecasts as
if we bootstrap the empirical data and reestimate the models.
Bootstrapping the forecasts makes the computations faster and easier,
but requires us to drop the first $R$ observations from the bootstrap
(the alternative forecasts are not defined for the first $R$
observations).  I add those observations to the beginning of each
bootstrap sample so that population means under the bootstrap-induced
probability distribution equal sample means.\footnote{This equality is
  strictly true only for the stationary and circular block
  bootstraps.}  The benchmark model still needs to be reestimated in
each bootstrap sample.

@@

\begin{rem}\label{rem:2}
  The key difference between conclusions~\ref{it:1} and~\ref{it:2} is
  that, in conclusion~\ref{it:2}, the forecast error is an \mds\ with
  respect to several individual series, but not necessarily with
  respect to the pooled information set generated by all of those
  series together.\footnote{It is straightforward to construct three
    series, $u_t$, $v_t$, and $w_t$, such that $w_t$ is an \mds\ with
    respect to $\sigma((u_t, w_t), (u_{t-1}, w_{t-1}),\dots)$ and
    $\sigma((v_t, w_t), (v_{t-1}, w_{t-1}),\dots)$ but not
    $\sigma((u_t, v_t, w_t), (u_{t-1}, v_{t-1}, w_{t-1}),\dots)$.
    This is essentially the scenario imposed in conclusion~\ref{it:2}.}
  Using $b = 1$ would consistently estimate the marginal distribution
  of each $\tfrac1{\sigma_i} \bar{f}_i$ under this weaker null
  hypothesis, but would not necessarily estimate the joint
  distribution of two or more of those terms correctly (in particular,
  the covariance could be wrong).  The stronger null hypothesis
  imposed in conclusion~\ref{it:1} ensures that resampling with $b = 1$
  estimates the joint distribution correctly as well.

@@

\begin{rem}\label{rem:01}
  \citet{Pin:11} raises the issue that, since there are often several
  models that could be used as the benchmark, researchers may want to
  control for data snooping over the null hypotheses as well as the
  alternatives.  For example, one could use either \citepos{AtO:01}
  random walk or \citepos{StW:07} \textsc{ima}(1,1) as benchmark
  inflation models, so it might make sense to require an alternative
  model to outperform them both.\footnote{\citet{Pin:11} studies tests
    that reject if the alternative model outperforms either of the
    models, so the details are somewhat different in our papers.}
  Allowing multiple benchmark models can be expressed as an
  Intersection-Union test, so Theorem~\ref{res:2}'s procedure
  (conclusion~\ref{it:3}) easily accommodates this extension by taking
  each $\bar f_i$ and $\hat{\sigma}_{i}^{2}$ to be a random
  $q$-vector;\footnote{If a researcher uses multiple benchmark models,
    it would be a mistake to assume that they are all correctly
    specified, so only the null hypothesis of conclusion~\ref{it:3} is
    appropriate.} the first element of $\bar f_{i}$, written as $\bar
  f_{i1}$, compares the first benchmark model to the $i$th alternative
  and the first element of $\hat{\sigma}_i^2$ is the corresponding
  estimate of asymptotic variance, the second element corresponds to
  the second benchmark model, etc.

@@

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item The estimator $\hat{\beta}_t$ of $\btrue$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k \times q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$; $H_{t}$ is a sequence of $q$-vectors such that
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}(\btrue) & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\btrue) & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}(\btrue) & \text{fixed window} \\
      \end{cases}
    \end{equation}
    and $\E h_{s}(\btrue) = 0$ for all $s$.
  \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
    $\psi_t(\beta)$ is covariance stationary and twice continuously
    differentiable in an open neighborhood $N$ of $\btrue$.  Also,
    $\E \sup_{\beta \in N} |\psi_t(\beta)|^r$ and $\E\sup_{\beta \in
      N} |\frac{\partial}{\partial \beta} \psi_t(\beta)|^r$ are
    uniformly bounded, and there exists a sequence of random variables
    $m_t$ such that $\sup_{i,\beta \in N} |\tfrac{\partial^2}{\partial
      \beta \partial \beta'} \psi_{it}(\beta)| \leq m_t$ almost surely
    and $\E m_t^2$ is uniformly finite.
  \item Both $\psi_t(\beta)$ and $\frac{\partial}{\partial \beta}
    \psi_t(\beta)$ are $L_2$-\ned\ of size $-\frac12$ on the
    series $V_t$ with bounded \ned-coefficients for $\beta$ uniformly
    in $N$; $V_t$ is strong mixing of size $-\frac{r}{r-2}$ or uniform
    mixing of size $-\frac{r}{2r-2}$ with $r > 2$.\footnote{For
      uniform mixing processes, $r = 2$ is also allowed as long as
      $\sup_{\beta \in N} \psi_t(\beta)^2$ and $\sup_{\beta \in N}
      (\partial \psi_t(\beta) / \partial \beta)^2$ are uniformly
      integrable.}
  \item The sequence $\hat f_1^{*},\dots,\hat f_T^{*}$ is constructed
    using the same procedure as the original \oos\ analysis over the
    bootstrap sample, where the bootstrap sample is generated by
    moving blocks, circular blocks, or stationary bootstrap with block
    lengths drawn from the geometric distribution.  The (expected)
    block length $b$ satisfies $b \to \infty$ and $\frac{b}{P} \to 0$.
  \item The bootstrapped estimator satisfies $\sup_t |\hat{B}_t^{*} -
    B^{*}| \to^p 0$, $B^{*} = B + o_p$ and $\frac1T \sum_{t=1}^T
    h_t^*(\btrue[*]) = 0$ a.s.
  \item The asymptotic variance matrix of $\bar{f}(\btrue)$ is
    uniformly positive definite.
  \item $R, P \to \infty$ as $T \to \infty$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\btrue[*]))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\btrue)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\begin{rem}
  \citet{Whi:00} and \citet{Han:05} resample the forecasts but do not
  reestimate any of them which requires the additional assumption that
  $\tfrac{P}{R} \log \log R \to 0$ or that the forecasts themselves
  have no estimated parameters.\footnote{\citet{Whi:00} lists several
    different sets of assumptions that give the same result, but these
    seem to be the most general.}
\end{rem}

>>>>

\date{March 14, 2013}

@@

\oos\ tests are commonly used in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.%
\footnote{Other papers in this literature include
  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:12,ClM:12b},
  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
  reviews of this literature and additional references, see
  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
  \citet{CoD:11}, and \citet{Gia:11}} %
In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a martingale difference sequence.  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic appropriately.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).%
\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.} %

@@

Mixing window strategies is uncommon but needn't be. In most
applications, the null hypothesis imposes stability as well as equal
accuracy between the two models.  The benchmark model rarely allows
for breaks, parameter drift, or other forms of
instability,%
\footnote{Exceptions are \citepos{StW:07}
  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} %
but the
researcher is typically concerned about instability.  Indeed, concern
about instability is often given as a reason for doing an \oos\
analysis, especially with a short rolling window.%
\footnote{This
  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
  \cite{GiR:09,GiR:10}, among others.} %
A researcher could impose
stability on both models by using a recursive window or relax
stability for both by using a rolling window; either approach should
not affect the test's size, but may affect power.  But the researcher
could instead impose stability on the benchmark and relax it for the
alternative by using a recursive window for the benchmark and a
rolling window for the alternative model.  This approach could have a
power advantage and is similar in spirit to using a Likelihood Ratio
Test instead of an \textsc{lm} or Wald test, which depend on just the
restricted or unrestricted model respectively.

@@

This paper focuses on nested models, as they have received the most
attention in the empirical and theoretical literature, but the
statistic can be used with non-nested models as well.  This generality
is useful, since \citepos{Wes:96} results do not apply to non-nested
models if they both encompass the true \dgp,%
\footnote{\citet{ClM:11b}
  call this scenario, ``overlapping models.''} %
which is allowable
under the null: in the limit, both models will converge to the \dgp\
and give identical forecasts.  Consequently, the naive \oos\ $t$-test
is invalid, even after correcting the standard error if necessary to
reflect parameter uncertainty.  \citet{ClM:11b} show that the fixed
window \oos\ $t$-test remains normal for these models but the
recursive and rolling windows (with the window size increasing to
$\infty$) do not, and provide a procedure for pointwise (but not
uniformly) valid tests for the recursive and rolling windows and
uniformly valid tests for the fixed window.  The test proposed in this
paper is uniformly valid and places fewer assumptions on the models
under study and the true \dgp.

@@

This paper also presents a new result for the validity of block
bootstraps with \oos\ statistics, which is necessary to verify that
the StepM is valid.  Existing results on bootstrapping \oos\
statistics have some drawbacks.  \citet{Whi:00} and \citet{Han:05} use
the stationary bootstrap, but require the test sample to be much
smaller than the training sample, which obviously does not hold here.
\citet{CoS:07} relax that requirement, but make the statistic more
complicated than necessary by adjusting the objective function of the
bootstrapped statistic to center it correctly.%
\footnote{Their
  recentering is required for consistency and does not imply higher
  order accuracy.} %
A parametric bootstrap, such as that used by
\cite{Mar:95}, \cite{Lut:99}, and \citet{ClM:12b}, is an alternative
method, but requires the benchmark model to be correctly specified.
Although I focus on the null hypothesis that the benchmark is
correctly specified, this paper's block bootstrap methods remain valid
when the benchmark is misspecified and are relatively easy to
implement.  So this paper's result for bootstrapping \oos\ statistics
considerably improves on existing procedures.

@@

\section{Out-of-Sample Model Comparisons}\label{sec:1}
This section presents the new \oos\ statistic.  I will present the
single-comparison statistic first and then extend it to multiple
comparisons.  Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
(Theorem~\ref{res:1} lists the assumptions formally).  In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudo-true
coefficient of the regression of $y_{t+1}$ on $x_t$ and define
$\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If the linear model is
correctly specified, so $\varepsilon_{t+1}$ is a martingale difference
sequence with respect to $\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t),
(x_{t-1}, v_{t-1}, y_{t-1}),\dots)$, then we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt\ (assuming that its variance is uniformly
positive) and is asymptotically normal as $P \to \infty$, with $R$ an
arbitrary starting value%
\footnote{It will be clear momentarily why the
  summation begins at $R+1$ instead of $1$.} %
and $P = T - R$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
\end{equation}

@@

\begin{rem}
  The statistic we present tests the null hypothesis that the forecast
  errors from the population version of the benchmark model are a
  martingale difference sequence.  This hypothesis may not be
  appropriate, depending on the loss function or utility function of
  interest.  If one wants to test the less restrictive null hypothesis that
  $y_{t} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$ but not
  necessarily an \mds, one can replace $\hat{S}_{ff}$, $\hat{S}_{fg}$
  and $\hat{S}_{gg}$ with their \hac\ counterparts.  
  Our statistic can also be modified to test implications of
  optimal forecasts under other loss functions
  \citep[see][]{PaT:07,PaT:07b}; the statistic should be expressed as
  a forecast encompassing test using the models' generalized forecast
  errors.%
\footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.} %
  Again, Lemma~\ref{res:a5} can cover these other applications.
\end{rem}

@@

Since most empirical papers study more than one alternative model,
Theorem~\ref{sec:1} is of limited use on its own.%
\footnote{Moreover,
  we would need to account for the existence of multiple models even if
each paper only considered a single model, since there are many papers
studying the same data.} %
It can, however, be
used as the basis for a procedure that allows researchers to make
multiple comparisons.  Before presenting a theoretical result, I will
discuss some issues related to multiple hypothesis testing.

Suppose we have the family of hypotheses, $H_1,\dots,H_J$.  It is
clear that testing each hypothesis individually will often have a
probability greater than the tests' nominal size of rejecting at least
once.%
\footnote{Unless the statistics used for each test are completely
  interdependent, the probability will be strictly greater than the
  nominal size.} %
Econometricians, e.g. \citet{Whi:00},
\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:12b}, have emphasized
statistics that test families of hypotheses that control the
probability any hypothesis is rejected given that they all are true,
known as \textit{weak control of familywise error}
(\wfwe).%
\footnote{An exception is \citet{HHK:10} who combine
  \citepos{RoW:05} StepM with \citepos{Han:05} threshold rule to
  control \sfwe\ for certain families of one-sided tests.} %
This paper
focuses instead on controlling the probability that at least one true
hypothesis is rejected given any combination of true and false
hypotheses, known as \textit{strong control of familywise error}
(\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
even though these papers only prove \wfwe, statistics based on
nonparametric block bootstraps \citep{Whi:00,Han:05} can be shown to
control \sfwe\ as well \citep[this follows directly from][]{RoW:05}
and those based on the parametric bootstrap \citep{ClM:12b} essentially
control \sfwe\ if the individual null hypotheses are strengthened
slightly as below (see conclusion~\ref{it:1} of Theorem~\ref{res:2} as
well as Remark~\ref{rem:2}).  \citet{HuW:10} propose that researchers
construct critical values from the asymptotic joint distribution of
the test statistics and this procedure can control \sfwe\ as long as there is a
consistent estimator of that distribution.

@@

This procedure exploits the fact that $R$ is finite in
Theorem~\ref{res:1} and that the expected block length will grow with
$T$.  Under these asymptotics, a growing proportion of the
rolling-window forecasts are the same if we bootstrap the forecasts as
if we bootstrap the empirical data and reestimate the models.
Bootstrapping the forecasts makes the computations faster and easier,
but requires us to drop the first $R$ observations from the bootstrap
(the alternative forecasts are not defined for the first $R$
observations).  I add those observations to the beginning of each
bootstrap sample so that population means under the bootstrap-induced
probability distribution equal sample means.%
\footnote{This equality is
  strictly true only for the stationary and circular block
  bootstraps.} %
The benchmark model still needs to be reestimated in
each bootstrap sample.

@@

\begin{rem}\label{rem:2}
  The key difference between conclusions~\ref{it:1} and~\ref{it:2} is
  that, in conclusion~\ref{it:2}, the forecast error is an \mds\ with
  respect to several individual series, but not necessarily with
  respect to the pooled information set generated by all of those
  series together.%
\footnote{It is straightforward to construct three
    series, $u_t$, $v_t$, and $w_t$, such that $w_t$ is an \mds\ with
    respect to $\sigma((u_t, w_t), (u_{t-1}, w_{t-1}),\dots)$ and
    $\sigma((v_t, w_t), (v_{t-1}, w_{t-1}),\dots)$ but not
    $\sigma((u_t, v_t, w_t), (u_{t-1}, v_{t-1}, w_{t-1}),\dots)$.
    This is essentially the scenario imposed in conclusion~\ref{it:2}.} %
  Using $b = 1$ would consistently estimate the marginal distribution
  of each $\tfrac1{\sigma_i} \bar{f}_i$ under this weaker null
  hypothesis, but would not necessarily estimate the joint
  distribution of two or more of those terms correctly (in particular,
  the covariance could be wrong).  The stronger null hypothesis
  imposed in conclusion~\ref{it:1} ensures that resampling with $b = 1$
  estimates the joint distribution correctly as well.

@@

\begin{rem}\label{rem:01}
  \citet{Pin:11} raises the issue that, since there are often several
  models that could be used as the benchmark, researchers may want to
  control for data snooping over the null hypotheses as well as the
  alternatives.  For example, one could use either \citepos{AtO:01}
  random walk or \citepos{StW:07} \textsc{ima}(1,1) as benchmark
  inflation models, so it might make sense to require an alternative
  model to outperform them both.%
\footnote{\citet{Pin:11} studies tests
    that reject if the alternative model outperforms either of the
    models, so the details are somewhat different in our papers.} %
  Allowing multiple benchmark models can be expressed as an
  Intersection-Union test, so Theorem~\ref{res:2}'s procedure
  (conclusion~\ref{it:3}) easily accommodates this extension by taking
  each $\bar f_i$ and $\hat{\sigma}_{i}^{2}$ to be a random
  $q$-vector;%
\footnote{If a researcher uses multiple benchmark models,
    it would be a mistake to assume that they are all correctly
    specified, so only the null hypothesis of conclusion~\ref{it:3} is
    appropriate.} %
  the first element of $\bar f_{i}$, written as $\bar
  f_{i1}$, compares the first benchmark model to the $i$th alternative
  and the first element of $\hat{\sigma}_i^2$ is the corresponding
  estimate of asymptotic variance, the second element corresponds to
  the second benchmark model, etc.

@@

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item The estimator $\hat{\beta}_t$ of $\btrue$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k \times q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$; $H_{t}$ is a sequence of $q$-vectors such that
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}(\btrue) & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\btrue) & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}(\btrue) & \text{fixed window} \\
      \end{cases}
    \end{equation}
    and $\E h_{s}(\btrue) = 0$ for all $s$.
  \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
    $\psi_t(\beta)$ is covariance stationary and twice continuously
    differentiable in an open neighborhood $N$ of $\btrue$.  Also,
    $\E \sup_{\beta \in N} |\psi_t(\beta)|^r$ and $\E\sup_{\beta \in
      N} |\frac{\partial}{\partial \beta} \psi_t(\beta)|^r$ are
    uniformly bounded, and there exists a sequence of random variables
    $m_t$ such that $\sup_{i,\beta \in N} |\tfrac{\partial^2}{\partial
      \beta \partial \beta'} \psi_{it}(\beta)| \leq m_t$ almost surely
    and $\E m_t^2$ is uniformly finite.
  \item Both $\psi_t(\beta)$ and $\frac{\partial}{\partial \beta}
    \psi_t(\beta)$ are $L_2$-\ned\ of size $-\frac12$ on the
    series $V_t$ with bounded \ned-coefficients for $\beta$ uniformly
    in $N$; $V_t$ is strong mixing of size $-\frac{r}{r-2}$ or uniform
    mixing of size $-\frac{r}{2r-2}$ with $r > 2$.%
\footnote{For
      uniform mixing processes, $r = 2$ is also allowed as long as
      $\sup_{\beta \in N} \psi_t(\beta)^2$ and $\sup_{\beta \in N}
      (\partial \psi_t(\beta) / \partial \beta)^2$ are uniformly
      integrable.} %
  \item The sequence $\hat f_1^{*},\dots,\hat f_T^{*}$ is constructed
    using the same procedure as the original \oos\ analysis over the
    bootstrap sample, where the bootstrap sample is generated by
    moving blocks, circular blocks, or stationary bootstrap with block
    lengths drawn from the geometric distribution.  The (expected)
    block length $b$ satisfies $b \to \infty$ and $\frac{b}{P} \to 0$.
  \item The bootstrapped estimator satisfies $\sup_t |\hat{B}_t^{*} -
    B^{*}| \to^p 0$, $B^{*} = B + o_p$ and $\frac1T \sum_{t=1}^T
    h_t^*(\btrue[*]) = 0$ a.s.
  \item The asymptotic variance matrix of $\bar{f}(\btrue)$ is
    uniformly positive definite.
  \item $R, P \to \infty$ as $T \to \infty$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\btrue[*]))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\btrue)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\begin{rem}
  \citet{Whi:00} and \citet{Han:05} resample the forecasts but do not
  reestimate any of them which requires the additional assumption that
  $\tfrac{P}{R} \log \log R \to 0$ or that the forecasts themselves
  have no estimated parameters.%
\footnote{\citet{Whi:00} lists several
    different sets of assumptions that give the same result, but these
    seem to be the most general.} %
\end{rem}
